Methods for Large Scale Learning to Rank

### 2014-11-20 report/Chapters/Implementation.tex
algorithms :)

\begin{algorithm}
REGISTER [path prefix]/lib/*.jar;\\
DEFINE QueryLossGradient udf.listnet.QueryLossGradient('[feature dimensionality of data set]');\\
DEFINE ExpRelOurScores udf.listnet.ExpRelOurScores('[neural network weights \& iteration number]');\\
$[$FIRST TRAINING ITERATION:$]$\\
\Indp
	TRAIN\_SCA = LOAD 'train\_sca[fold number]/*' USING BinStorage();\\
	TR\_BY\_QUERY = GROUP TRAIN\_SCA BY \$1 PARALLEL [number of avaiable reducers];\\
	TR\_EXP\_REL\_SCORES = FOREACH TR\_BY\_QUERY GENERATE flatten(ExpRelOurScores(TRAIN\_SCA));\\
	STORE TR\_EXP\_REL\_SCORES INTO 'tr\_exp\_rel\_scores-f[fold number]' USING BinStorage();\\
\Indm 
$[$SUBSEQUENT TRAINING ITERATIONS:$]$\\
\Indp
TR\_EXP\_REL\_SCORES = LOAD 'tr\_exp\_rel\_scores-f[fold number]/*' USING BinStorage();\\
TR\_EXP\_REL\_SCORES = FOREACH TR\_EXP\_REL\_SCORES GENERATE flatten(ExpRelOurScores(*)) PARALLEL [number of available reducers];\\
\Indm
TR\_QUERY\_LOSS\_GRADIENT = FOREACH TR\_EXP\_REL\_SCORES GENERATE flatten(QueryLossGradient(*)) PARALLEL [number of available reducers];\\
TR\_QUERY\_LOSS\_GRADIENT\_GRPD = GROUP TR\_QUERY\_LOSS\_GRADIENT ALL;\\
TR\_LOSS\_GRADIENT = FOREACH TR\_QUERY\_LOSS\_GRADIENT\_GRPD GENERATE flatten(udf.listnet.MultiSum(*));\\
STORE TR\_LOSS\_GRADIENT INTO 'tr\_loss\_gradient-f[fold number]i[iteration number]';\\
\caption{The second Pig job of the normalisation preprocessing procedure}
\label{alg:pig_listnet_1}
\end{algorithm}

@@

\begin{algorithm}
REGISTER [path prefix]/lib/*.jar;\\
DEFINE Ndcg udf.util.Ndcg('[neural network weights \& NDCG cut-off parameter]');\\
$[$FIRST TRAINING ITERATION:$]$\\
\Indp
	VALIDATE\_SCA = LOAD 'validate\_sca[fold number]/*' USING BinStorage();\\
	VA\_BY\_QUERY = GROUP VALIDATE\_SCA BY \$1 PARALLEL [number of available reducers];\\
	STORE VA\_BY\_QUERY INTO 'va\_by\_query-f[fold number]' USING BinStorage();\\
\Indm 
$[$SUBSEQUENT TRAINING ITERATIONS:$]$\\
\Indp
VA\_BY\_QUERY = LOAD 'va\_by\_query-f[fold number]/*' USING BinStorage();\\
\Indm 
NDCG = FOREACH VA\_BY\_QUERY GENERATE Ndcg(*);\\
NDCG\_GRPD = GROUP NDCG ALL;\\
AVG\_NDCG = FOREACH NDCG\_GRPD GENERATE AVG(NDCG);\\
STORE AVG\_NDCG INTO 'avg\_ndcg-f[fold number]i[iteration number]';\\
\caption{The second Pig job of the normalisation preprocessing procedure}
\label{alg:pig_listnet_2}
\end{algorithm}

@@

\subsection{Testing}
The testing stage tests the best model found in the training iterations, selected on validation set \ac{NDCG}@k (as calculated in the second Pig job of the training stage), by calculating the \ac{NDCG}@k of this model on the test set.\\

Test stage Pig job:\\
\begin{minipage}{\linewidth}
\begin{lstlisting}
REGISTER [path prefix]/lib/*.jar;
TEST_SCA = LOAD 'test_sca[fold number]/*' USING BinStorage();
TE_BY_QUERY = GROUP TEST_SCA BY $1 PARALLEL [number of available reducers];
DEFINE Ndcg udf.util.Ndcg('[neural network weights & NDCG cut-off parameter]');
NDCG = FOREACH TE_BY_QUERY GENERATE Ndcg(*);
NDCG_GRPD = GROUP NDCG ALL;
AVG_NDCG = FOREACH NDCG_GRPD GENERATE AVG(NDCG);
STORE AVG_NDCG INTO 'avg_ndcg';
\end{lstlisting}
\end{minipage}\\

>>>>

\begin{algorithm}
REGISTER [path prefix]/lib/*.jar;\\
DEFINE QueryLossGradient udf.listnet.QueryLossGradient('[feature dimensionality of data set]');\\
DEFINE ExpRelOurScores udf.listnet.ExpRelOurScores('[neural network weights \& iteration number]');\\
$[$FIRST TRAINING ITERATION:$]$\\
\Indp
	TRAIN\_SCA = LOAD 'train\_sca[fold number]/*' USING BinStorage();\\
	TR\_BY\_QUERY = GROUP TRAIN\_SCA BY \$1 PARALLEL [number of avaiable reducers];\\
	TR\_EXP\_REL\_SCORES = FOREACH TR\_BY\_QUERY GENERATE flatten(ExpRelOurScores(TRAIN\_SCA));\\
	STORE TR\_EXP\_REL\_SCORES INTO 'tr\_exp\_rel\_scores-f[fold number]' USING BinStorage();\\
\Indm 
$[$SUBSEQUENT TRAINING ITERATIONS:$]$\\
\Indp
TR\_EXP\_REL\_SCORES = LOAD 'tr\_exp\_rel\_scores-f[fold number]/*' USING BinStorage();\\
TR\_EXP\_REL\_SCORES = FOREACH TR\_EXP\_REL\_SCORES GENERATE flatten(ExpRelOurScores(*)) PARALLEL [number of available reducers];\\
\Indm
TR\_QUERY\_LOSS\_GRADIENT = FOREACH TR\_EXP\_REL\_SCORES GENERATE flatten(QueryLossGradient(*)) PARALLEL [number of available reducers];\\
TR\_QUERY\_LOSS\_GRADIENT\_GRPD = GROUP TR\_QUERY\_LOSS\_GRADIENT ALL;\\
TR\_LOSS\_GRADIENT = FOREACH TR\_QUERY\_LOSS\_GRADIENT\_GRPD GENERATE flatten(udf.listnet.MultiSum(*));\\
STORE TR\_LOSS\_GRADIENT INTO 'tr\_loss\_gradient-f[fold number]i[iteration number]';\\
\caption{The first Pig job of the ListNet training procedure}
\label{alg:pig_listnet_1}
\end{algorithm}

@@

\begin{algorithm}
REGISTER [path prefix]/lib/*.jar;\\
DEFINE Ndcg udf.util.Ndcg('[neural network weights \& NDCG cut-off parameter]');\\
$[$FIRST TRAINING ITERATION:$]$\\
\Indp
	VALIDATE\_SCA = LOAD 'validate\_sca[fold number]/*' USING BinStorage();\\
	VA\_BY\_QUERY = GROUP VALIDATE\_SCA BY \$1 PARALLEL [number of available reducers];\\
	STORE VA\_BY\_QUERY INTO 'va\_by\_query-f[fold number]' USING BinStorage();\\
\Indm 
$[$SUBSEQUENT TRAINING ITERATIONS:$]$\\
\Indp
VA\_BY\_QUERY = LOAD 'va\_by\_query-f[fold number]/*' USING BinStorage();\\
\Indm 
NDCG = FOREACH VA\_BY\_QUERY GENERATE Ndcg(*);\\
NDCG\_GRPD = GROUP NDCG ALL;\\
AVG\_NDCG = FOREACH NDCG\_GRPD GENERATE AVG(NDCG);\\
STORE AVG\_NDCG INTO 'avg\_ndcg-f[fold number]i[iteration number]';\\
\caption{The second Pig job of the ListNet training procedure}
\label{alg:pig_listnet_2}
\end{algorithm}

@@

\subsection{Testing}
The testing stage tests the best model found in the training iterations, selected on validation set \ac{NDCG}@k (as calculated in the second Pig job of the training stage), by calculating the \ac{NDCG}@k of this model on the test set. Algorithm \ref{alg:pig_test} describes the Pig code for model evaluation on the test data set.\\

\begin{algorithm}
REGISTER [path prefix]/lib/*.jar;\\
TEST\_SCA = LOAD 'test\_sca[fold number]/*' USING BinStorage();\\
TE\_BY\_QUERY = GROUP TEST\_SCA BY \$1 PARALLEL [number of available reducers];\\
DEFINE Ndcg udf.util.Ndcg('[neural network weights \& NDCG cut-off parameter]');\\
NDCG = FOREACH TE\_BY\_QUERY GENERATE Ndcg(*);\\
NDCG\_GRPD = GROUP NDCG ALL;\\
AVG\_NDCG = FOREACH NDCG\_GRPD GENERATE AVG(NDCG);\\
STORE AVG\_NDCG INTO 'avg\_ndcg';
\caption{The Pig job for model evaluation}
\label{alg:pig_test}
\end{algorithm}
